---
author: "Blake H Massey"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
knit: (function(inputFile, encoding) { 
  rmarkdown::render(inputFile, encoding = encoding, 
    output_file = file.path("C:/Users/blake/Desktop/Slidy_Presentations", 
    "Test Examples - Maps.html"))})
output: 
  slidy_presentation:
    theme: flatly
    font_adjustment: +2
    keep_md: no
    css: "Assets/CSS/style_helvetica.css"
params:
title: "Test Examples - Maps"  
---
<div class = "row">
<div class = "col-md-4">

<br><br>
Since R Markdown use the bootstrap framework under the hood. It is possible to 
benefit its powerful grid system. Basically, you can consider thatyour row is 
divided in 12 subunits of same width. You can then choose to use only a few of 
this subunits.
</div>
  
<div class = "col-md-4">
<br><br>
Here, I use 3 subunits of size 4 (4x3=12). The last column is used for 
a plot. You can read more about the grid system [here](bootstrap grid system). 
I got this result showing the following code in my R Markdown document.
</div>
  
<div class = "col-md-4">
```{r echo=FALSE, message=FALSE}
pacman::p_load(ggplot2)
#ggplot(mtcars, aes(x=mpg)) + 
#  geom_histogram(fill="skyblue", alpha=0.5) + 
#  theme_minimal()

library(sf)
library(mapview)
nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)
map1 <- mapview(nc, col.regions = "blue")
map2 <- mapview(nc, col.regions = "red")
leafsync::sync(map1, map2)

```
</div>
</div>

***
<center>
```{r echo=F, message=F, warning=FALSE, fig.width=8}
library(sf)
library(mapview)
nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)
mapview(nc)
```
</center>

***
<center>
```{r echo=F, message=F, warning=FALSE, fig.width=8}
library(sf)
library(mapview)
nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)
map1 <- mapview(nc, col.regions = "blue")
map2 <- mapview(nc, col.regions = "red")
leafsync::sync(map1, map2)
```
</center>
