---
title: "Test Examples - Text, Maps, Columns"  
author: "Blake H Massey"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
knit: (function(inputFile, encoding) { 
  rmarkdown::render(inputFile, encoding = encoding, 
    output_file = file.path("C:/Users/blake/Desktop/Slidy_Presentations", 
    "Test Examples - Text Maps Cols.html"))})
output: 
  slidy_presentation:
    theme:
    font_adjustment: 0
    keep_md: false
    css: "Assets/CSS/style_helvetica.css"
---

# List of items.

 - One
 - Two
 - Three

# Header 1  

## Heading 2.1  
 
<h2 class="leftalign">Heading 2.2</h2>

<h2 class="rightalign">Heading 2.3</h2>

     
### Heading 3  

#### Heading 4  

##### Heading 5  

###### Heading 6  

# Font Sizes

Standard font

- <span style="color:red">Change the font colour</span>
- <font size="1">This is some text size 1!</font>
- <font size="2">This is some text size 2!</font>
- <font size="3">This is some text size 3!</font>
- <font size="4">This is some text size 4!</font>
- <font size="5">This is some text size 5!</font>

***

<div class='left' style='float:left;width:48%;height:45%'>
## Header 2  
<br>
Since R Markdown use the bootstrap framework under the hood. It is possible to 
benefit its powerful grid system. Basically, you can consider thatyour row is 
divided in 12 subunits of same width. You can then choose to use only a few of 
this subunits.
</div>

<div class='right' style='float:right;width:48%;height:45%'>
### Header 3  

```{r echo=FALSE, message=FALSE}
pacman::p_load(ggplot2)
#ggplot(mtcars, aes(x=mpg)) + 
#  geom_histogram(fill="skyblue", alpha=0.5) + 
#  theme_minimal()

library(sf)
library(mapview)
nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)
map1 <- mapview(nc, col.regions = "blue")
map2 <- mapview(nc, col.regions = "red")
leafsync::sync(map1, map2)

```
</div>

<div class='left' style='float:left;width:48%'>
## Header 2  REPEATED  
<br>
Since R Markdown use the bootstrap framework under the hood. It is possible to 
benefit its powerful grid system. Basically, you can consider thatyour row is 
divided in 12 subunits of same width. You can then choose to use only a few of 
this subunits.
</div>

<div class='right' style='float:right;width:48%'>

### Header 3 REPEATED  

```{r echo=FALSE, message=FALSE}
pacman::p_load(ggplot2)
#ggplot(mtcars, aes(x=mpg)) + 
#  geom_histogram(fill="skyblue", alpha=0.5) + 
#  theme_minimal()

library(sf)
library(mapview)
nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)
map1 <- mapview(nc, col.regions = "blue")
map2 <- mapview(nc, col.regions = "red")
leafsync::sync(map1, map2)

```
</div>


***

#### Heading 4

<center>
```{r echo=F, message=F, warning=FALSE, fig.width=8}
library(sf)
library(mapview)
nc <- sf::st_read(system.file("shape/nc.shp", package = "sf"), quiet = TRUE)
map1 <- mapview(nc, col.regions = "blue")
map2 <- mapview(nc, col.regions = "red")
leafsync::sync(map1, map2)
```
</center>
